CUNY SPSS Data Science Math Homework 3

### 2018-07-23 data-science-math/Homework 3.Rmd
Additional Work on HW3

@@

@@

@@

@@

@@

@@

>>>>

```{r}
m <- 13000 
sd <- 40000**(1/2)
round(1-pnorm(979, m, sd), 4)
```

@@

```{r}
m <- 11000 
sd <- 1960000 **(1/2)
round(1-pnorm(8340, m, sd), 4)
```

@@

```{r}
m <- 80 
sd <- 3
round(1 - pnorm(83, m, sd) - (1-pnorm(85, m, sd)), 4)
```

@@

```{r}
m <- 456 
sd <- 123
p <- 14/100
round(qnorm(p, m, sd, lower.tail = FALSE), 0)
```

@@

```{r}
m <- 6.13 
sd <- 0.06
p <- 7/100
round(qnorm(p, m, sd), 3)
round(qnorm(p, m, sd, lower.tail = FALSE), 3)
```

@@

```{r}
m <- 78.8 
sd <- 9.8
round(qnorm((20/100), m, sd), 0)
round(qnorm((45/100), m, sd, lower.tail = FALSE), 0)
```

@@

```{r}
m <- 21.2 
sd <- 5.4
p <- 45/100
round(qnorm(p, m, sd, lower.tail = FALSE), 1)
```
